### 2016-07-05 filters.tex
adding side-information to syntax

By allowing $\Rep$ to output side-information, we allow for (say) $\Rep$ and $\Qry$ to share a secret key selected during representation generation.\tsnote{Ultimately it might be cleaner to fold the hash functions into the side-information, too.  But in that case, we will likely want an explicit separation between private side-information (e.g. the key for a secret permutation of the bits of~$M$) and public side-information (e.g. the hash functions used to create~$M$).  For now, since the only public side-information I see in the literature are the hash functions, I'm leaving it as is.}

@@

\begin{figure}
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPSecHash{B}{\distr{U}{n},A}$}\\
$S \getsr \distr{U}{n}$\\
$h_1,\ldots,h_k \getsr \Hash$\\
$\HashOracle = (h_1, \ldots, h_k)$\\
$M \getsr \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}(S)$\\
if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPPubHashBB{B}{\distr{U}{n}, A}$}\\
$S \getsr \distr{U}{n}$\\
$h_1,\ldots,h_k \getsr \Hash$\\
$\HashOracle = (h_1, \ldots, h_k)$\\
$M \getsr \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle,\HashOracle}(S)$\\
if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPPubHash{B}{\distr{U}{n}, A}$}\\
$S \getsr \distr{U}{n}$\\
$h_1,\ldots,h_k \getsr \Hash$\\
$\HashOracle = (h_1, \ldots, h_k)$\\
$M \gets \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\

>>>>

By allowing $\Rep$ to output side-information, we allow for (say) $\Rep$ and $\Qry$ to share a secret key selected during representation generation.\tsnote{Ultimately it might be cleaner to fold the hash functions into the side-information, too.  But in that case, we will likely want an explicit separation between private side-information (e.g. the key for a secret permutation of the bits of~$M$) and public side-information (e.g. the hash functions used to create~$M$).  For now, since the only public side-information I see in the literature are the hash functions, I'm leaving it as is.}  In our security notions, any side-information will be kept secret from the adversary.

@@

\begin{figure}
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPSecHash{B}{\distr{U}{n},A}$}\\
$S \getsr \distr{U}{n}$\\
$h_1,\ldots,h_k \getsr \Hash$\\
$\HashOracle = (h_1, \ldots, h_k)$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}(S)$\\
if $x \not\in S \wedge \Qry^{\HashOracle}(M,\tau,x)=1$ then\\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPPubHashBB{B}{\distr{U}{n}, A}$}\\
$S \getsr \distr{U}{n}$\\
$h_1,\ldots,h_k \getsr \Hash$\\
$\HashOracle = (h_1, \ldots, h_k)$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle,\HashOracle}(S)$\\
if $x \not\in S \wedge \Qry^{\HashOracle}(M,\tau,x)=1$ then\\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpFPPubHash{B}{\distr{U}{n}, A}$}\\
$S \getsr \distr{U}{n}$\\
$h_1,\ldots,h_k \getsr \Hash$\\
$\HashOracle = (h_1, \ldots, h_k)$\\
$(M,\tau) \gets \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
if $x \not\in S \wedge \Qry^{\HashOracle}(M,\tau,x)=1$ then\\
\nudge Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
